Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Research questions

@@

\subsubsection{Thresholds}\label{chap:thresholds}
CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).

@@

\section{Relation, Location and Content Analysis of Clones}\label{chap:clonecontextexpl}
To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
  \item The contents of a clone instance (for example: the clone instance spans several methods).
\end{enumerate}

>>>>

\subsection{Research questions}
We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:

\textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
\textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?

@@

\section{Thresholds}\label{chap:thresholds}

CloneRefactor works on basis of three thresholds for finding clones:
\begin{enumerate}
  \item \textbf{Number of statements/declarations:} The number of statements/declarations that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of tokens:} The number of tokens (excluding whitespace, end-of-line terminators and comments) that should be equal/similar for it to be considered a clone.
  \item \textbf{Number of lines:} The minimum amount of lines (excluding lines that do not contain any tokens) that should be equal/similar for it to be considered a clone.
\end{enumerate}
Of course, if any threshold is set to zero, it will be ignored, thus not all thresholds have to be used at all times. We consider ``number of lines'' to be the least important, as it highly depends on the developer of the codebase (and we want to prevent this dependence).

@@

\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
To be able to refactor code clones, it is very important to consider the context of the clone. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item The relation of clone instances among each other through inheritance (for example: a clone instance resides in a superclass of another clone instance in the same clone class).
  \item Where a clone instance occurs in the code (for example: a method-level clone is a clone instance that is in a method).
  \item The contents of a clone instance (for example: the clone instance spans several methods).
\end{enumerate}
